---
title: "MATH 3070 Lab Project 3"
author: "Your Name"
date: "June 1, 2022"
output:
  pdf_document:
    toc: yes
  html_document:
    toc: yes
---

*Remember: I expect to see commentary either in the text, in the code with comments created using `#`, or (preferably) both! **Failing to do so may result in lost points!***



## Problem 1 (Verzani problem 2.34)
*The data set `DDT` (**MASS**) contains independent measurements of the pesticide DDT on kale. Make a histogram and a boxplot of the data. From these, estimate the mean and standard deviation. Check your answers with the appropriate functions.*

```{r}
# Your code here
```

## Problem 2 (Verzani problem 2.32 modified)
*Write a function 'density_compare()' that fits a density estimate to a given data set and plots that estimate along with the appropriate histogram of the given data set. Try your function with the data set `pi2000` (**UsingR**). Why might you want to add an argument like `breaks = 0:10-.5` to `hist()`? (Hint: read the documentation of `hist()` to see what setting this argument does). Feel free to add other parameters to your plot methods to see how they can be changed.*

```{r}
# Your code here
```

## (BONUS) Problem 3 (Verzani problem 2.43)
*The `time` variable in the `nym.2002` data set (**UsingR**) contains the time to finish the 2002 New York City Marathon for a random sample of the finishers.*

1. *What percent ran the race in under 3 hours? (note that the data is in minutes)*

```{r}
#library(UsingR) 
#your code here

```

2. *What is the time cutoff for the top 10%? The top 25%?*

```{r}
# Notice that these are the 10th and 25th percentiles, respectively
# Your code here
```

3. *What time cuts off the bottom 10%?*

```{r}
# Your code here
```


## Problem 4 (Verzani problem 4.1)
*The data set `UScereal` (**MASS**) contains data on cereals sold in the United States in 1993. For this data set, answer the following questions using R (i.e. MUST answer questions using a code. Do not count by hand):*

1. *How many rows does the data frame have? Columns?*

```{r}
# Your code here
```

2. *How many different manufacturers are included?*

```{r}
# Your code here
```

3. *How many vitamin categories are included?*

```{r}
# Your code here
```

4. *How many cereals have a sugar level above 10?*

```{r}
# Your code here
```

5. *What is the mean calorie value for cereals with more than 5 grams of fat? Less than or equal to 5?*

```{r}
# Your code here
```

6. *What is the mean calorie value for cereals on the middle shelf (2)?*

```{r}
# Your code here
```

## Problem 5: Create a Data Frame
*Create a data frame containing the data in the following table:*

| First    | Last      | Age |
|----------|-----------|-----|
| Marcus   | Holstein  | 23  |
| Samuel   | Adams     | 56  |
| Gus      | McPherson | 43  |
| Margaret | Olsen     | 41  |
| Zim      | Newbold   | 95  |

```{r}
# Your code here
```
