---
title: "MATH 3070 Lab Project 07"
author: "Maria R Bazaldua"
date: "June 29, 2022"
output:
  pdf_document:
    toc: yes
  html_document:
    toc: yes
---

*Remember: I expect to see commentary either in the text, in the code with comments created using `#`, or (preferably) both! **Failing to do so may result in lost points!***


## Problem 1 (Verzani problem 3.20)
*The `batting` (**UsingR**) data set contains baseball statistics for the 2002 Major League Baseball season. What is the correlation between the number of strikeouts (`SO`) and the number of home runs (`HR`)? Make a scatter plot to see whether there is any trend. Does the data suggest that in order to hit a lot of home runs one should strike out a lot?*

```{r, tidy=TRUE, message=FALSE}
# Your code here
library(UsingR) #acquiring the data for batting
data <- batting #setting the batting data to the variable data 
cor(batting$SO, batting$HR) #using COR function in R to find correlation 

library(ggplot2)
ggplot(batting, aes(x = SO, y = HR)) + geom_point() + labs(title = "Correlation Between Home Runs and Strikeouts", x = "Strikeouts", y = "Home Runs") #using ggplot to graph scatter plot and see correlation between HR and SO 

#The data suggests that you do NOT necessarily need to strikeout often in order to get a lot of home runs. If a batter struck out more than 150 times, it did not necessarily increase their changes of getting a home run. Overall, there appears there is no strong correlation with high strike outs and more home runs. 

```

## Problem 2 (Verzani problem 3.32)
*The data set `UScereal` (**MASS**) contains information about cereals on a shelf of a United States grocery store. Make a table showing the relationship between manufacturer, `mfr`, and shelf placement, `shelf`. Are there any obvious differences between manufacturers?*

```{r, tidy=TRUE, message=FALSE}
# Your code here
install.packages("MASS") #installing required package 
library(MASS) #acquiring UScereal data 

cereal <- UScereal #setting UScereal data to the variable cereal 

mfr_shelf_tab <- xtabs(~mfr+shelf, data = cereal) #creating a tab for manufacturer and shelf 
ftable(mfr_shelf_tab) #using the ftable function to make a table by mfr and shelf 

#The manufacturer K and G take up the most placements in shelf 1, 2, and 3. The rest of the manufacturers have less placements on each of the 3 shelves. 

```

## Problem 3 (Verzani problem 3.33)
*The help page for `mosaicplot()` demonstrates the data set `HairEyeColor`, which records `sex`, `Hair` color, and `Eye` color for 592 statistics students. The data set comes as a flattened table, so simply passing the object to `mosaicplot()` will create the plot. (Or, as demonstrated, passing `shade = TRUE`, as in `mosaicplot(HairEyeColor, shade = TRUE)`, will produce a colored version.)*
*Make the plot. Why does the help page note, "there are more blue-eyed, blonde females than expected?"*

```{r, tidy=TRUE, message=FALSE}
# Your code here
require(stats) #acquiring the data set 
mosaicplot(HairEyeColor, shade = TRUE) #plotting the data set as shown in the help page 
```

## Problem 4 (Verzani problem 6.2)
*Roll a pair of dice. Let $X$ be the largest value shown on the two dice. Use `sample()` to simulate five values of $X$.*

```{r, echo=FALSE, message=FALSE}
# This code block resets the random seed in order to get consistent results. This will be hidden in the final document, but YOU MUST NOT CHANGE THIS!
set.seed(5292016)
```

```{r, error=TRUE, tidy=TRUE, message=FALSE}
# Your code here
```

## Problem 5 (Verzani problem 6.3)
*The National Basketball Association lottery to award the first pick in the draft is held by putting 1,000 balls into a hopper and selecting one. The teams with the worst records the previous year have a greater proportion of the balls. The data set `nba.draft` (**UsingR**) contains the ball allocation for the year 2002. Use `sample()` with Team as the data vector and `prob=Balls` to simulate the draft. What team do you select? Repeat until Golden State is chosen. How long did it take?*

```{r, echo=FALSE, message=FALSE}
# This code block resets the random seed in order to get consistent results. This will be hidden in the final document, but YOU MUST NOT CHANGE THIS!
set.seed(5292016)
```

```{r, error=TRUE, tidy=TRUE}
# Your code here
```
