---
title: "MATH 3070 Lab Project 10"
author: "Maria R Bazaldua"
date: "Due Date: July 21, 2022"
output:
  html_document:
    toc: yes
  pdf_document:
    toc: yes
---

*Remember: I expect to see commentary either in the text, in the code with comments created using `#`, or (preferably) both! **Failing to do so may result in lost points!***


## Problem 1 (Verzani problem 9.14)
*The data set `normtemp` (**UsingR**) contains measurements of 130 healthy, randomly selected individuals. The variable `temperature` contains normal body temperature. Does the data appear to come from a Normal distribution? If so, perform a $t$-test to see if the commonly assumed value of 98.6 degrees fahrenheit is correct. (Studies have suggested that 98.2 degrees fahrenheit is more accurate.)*

```{r, tidy = TRUE}
# Your code here

install.packages("UsingR") #installing Using R package for problem 1
library(UsingR) #acquiring the data from the UsingR

data <- normtemp
temp <- normtemp$temperature
qqnorm(temp) #using qqnorm to see if distribution appears to be approx. normal 

#distribution is approx norm
t.test(temp, mu = 98.6) #using t.test R function to determine if mu = 98.6
#based on our evidence and default alpha of .05, we reject H null as the true range is below 98.6 

```



## Problem 2 (Verzani problem 9.4)
*In the United States in 2007, the proportion of adults age 21-24 who had no medical insurance was 28.1 percent. A survey of 75 recent college graduates in this age range finds that 40 percent are without insurance. Does this support a difference from the nationwide proportion? Perform a test of significance and report the p-value. Is it significant? (Perform this test "by hand", not using `prop.test()`.)*

```{r, tidy = TRUE}
# Your code here

phat <- .40 #forty percent of the 75 surveyed students do not have insurance
n <- 75
usp <- 28.1

#p times 1 - p all divided by 75
denom <- .281*.719/75
denom

z <- (.40 - .281)/sqrt(denom) #using z test for significance testing 
z

pval <- 2*(1-pnorm(abs(z))) #using R functions to calculate p value 
pval

#based on our evidence at default alpha .05 we reject h null since .02 is less, the proportion of college students surveyed were more likely to not have insurance than the general population

```

## Problem 3 (Verzani problem 9.16)
*A one-sided, one-sample $t$-test will be performed. What sample size is needed to have a power of 0.80 for a significance level of 0.05 if `delta = 0.05` and the population standard deviation is assumed to be 5?*

```{r, tidy = TRUE}
# Your code here

power.prop.test(power = .80, p1 = .05, p2 = .051, alternative = c("one.sided")) #using R function to find n needed for survey, in order to find n we also need a p2 value 

```

## Problem 4 (Verzani problem 9.31)
*For the `babies` (**UsingR**) data set, the variable `age` contains the recorded mom's age and `dage` contains the dad's age for several cases in the sample. Do a significance test of the null hypothesis of equal ages against a one-sided alternative that the dads are older in the sampled population.*

```{r, tidy = TRUE}
# Your code here

momage <- babies$age
dadage <- babies$dage

t.test(momage, dadage, alternative = "two.sided", conf.level = .05) #using two sided to t.test to compare to t.test for greater, this t.test shows that there is a difference in means 

t.test(momage, dadage, alternative = "greater", conf.level = .05) #this t. test shows that the dad's age is greater than the mom's age 



```