---
title: "MATH 3070 Lab Project 09"
author: "Maria R Bazaldua"
date: "Release Date: July 13, 2022 "
output:
  html_document:
    toc: yes
  pdf_document:
    toc: yes
---

*Remember: I expect to see commentary either in the text, in the code with comments created using `#`, or (preferably) both! **Failing to do so may result in lost points!***


## Problem 1 (Verzani problem 8.7)
*Of the last ten times you've dropped your toast, it landed sticky-side down nine times. If these are a random sample from the $\text{Ber}(p)$ distribution, find an 80% confidence interval for $p$, the probability of the stidy side landing down. (Use `binconf()` (**Hmisc**) to compute the score interval.)*

```{r, tidy = TRUE}
# Your solution here

install.packages("Hmisc") #downloading the Hmsic package
library(Hmisc) #obtaining the information inside the package
binconf(9, 10, alpha = .20, method = "wilson") #binconf function finds the two tailed confidence 

```

## Problem 2 (Verzani problem 8.10)
*A survey is taken of 250 students, and a $\hat{p}$ of 0.45 is found. The same survey is repeated with 1000 students, and the same $\hat{p}$ is found. Compare the two 95% confidence intervals. What is the relationship? Is the margin of error for the second one four times smaller? If not, how much smaller is it? (Use `binom.test()` to answer this problem.)*

```{r, tidy = TRUE}
# Your solution here
x1 <- .45*250
x1
binom.test(ceiling(x1), 250, alternative = "greater", conf.level = .95)

binom.test(450, 1000, alternative = "greater", conf.level = .95)

```

## Problem 3 (Verzani problem 8.14)
*The `stud.recs` (**UsingR**) data set contains a sample of math SAT scores from some population in the variable `sat.m`. Find a 90% confidence interval for the mean math SAT score for this data. (Do not use `t.test(); find this confidence interval "by hand".)*

```{r, tidy = TRUE}
# Your solution here

install.packages("UsingR") #downloading the UsingR package
library(UsingR) #obtaining the information inside the package
sat <- stud.recs$sat.m

xbar <- mean(sat)
zstar <- qnorm(.05) #two tailed test 
sigma <- .10
moe <- zstar*sigma/sqrt(length(sat))

ci <- c("Lower" = xbar - moe, "Upper" = xbar+moe)
ci

```

## Problem 4 (Verzani problem 8.15)
*For the `homedata` (**UsingR**) data set find 90% confidence intervals for both variables `y1970` and `y2000`, assuming the sample represents some population. Perform one sample t-test for each variable, use `t.test()`, but first discuss whether the model assumptions are appropriate (include some check of the assumptions, like a Q-Q plot).*

```{r, tidy = TRUE}
# Your solution here

y1 <- homedata$y1970 #setting the homedata of 1970 to y1
y2 <- homedata$y2000 #setting the homedata of 2000 to y2

t.test(y1, conf.level = .90) #using t.test function to find the C.I interval
t.test(y2, conf.level = .90) #finding C.I interval for y2

qqnorm(y1, main = "Normal QQ Plot for Y1") #plotting y1 to find distribution
qqline(y1)

qqnorm(y2, main="Normal QQ Plot for Y2") #plotting y2 to find distribution
qqline(y1)

#to use the t.test we need to have an approximately normal distribution, small sample, and unknown sigma, therefore, it makes sense to use the t.test for homedata$1970 because the distribution is approximately normal. However, the distribution for homedata$2000 strays away from the normal line more and likely does not have a normal distribution. 

```