---
title: "MATH 3070 Lab Project 06"
author: "Maria R Bazaldua"
date: "June 22, 2022"
output:
  pdf_document:
    toc: yes
  html_document:
    toc: yes
---

*Remember: I expect to see commentary either in the text, in the code with comments created using `#`, or (preferably) both! **Failing to do so may result in lost points!***


## Problem 1 (Verzani problem 3.2)
*For the `michelson` (**MASS**) data set, produce a density plot comparing `Speed` between Experiments 1 and 2.*

```{r, tidy=TRUE, error=TRUE}
# Your code here
install.packages("MASS")
library(MASS)
mike1 <- subset(michelson, select = Speed, subset = Expt == 1)
mike2 <- subset(michelson, select = Speed, subset = Expt == 2)

den_m1 <- density(unlist(mike1))
den_m2 <- density(unlist(mike2))

plot(den_m1, col = "red", ylim = c(0, .006), xlab = "Speed", main = "Density Plot Comparing Experiment 1 & 2")
lines(den_m2, col = "green")
legend(1100, .005, legend = c("Exp1", "Exp2"), col = c("red", "green"), lty = 1.5, cex = 1)


```

## Problem 2 (Verzani problem 3.4)
*Three students record the time spent on homework per class. Their data is:*

| Student| 1  | 2  | 3  | 4  | 5 |
|:-------|---:|---:|---:|---:|--:|
| Marsha | 25 | 0  | 45 | 90 | 0 |
| Bill   | 30 | 30 | 30 | 30 |   |
| Holly  | 15 | 0  | 90 | 0  |   |

*Use a list to store these values. Then create a boxplot to compare. (You must use `boxplot()`'s formula interface for this problem.)*

```{r, tidy=TRUE, error=TRUE}
# Your code here
students <- c("Marsha", "Bill", "Holly")

Marsha <- c(25, 0, 45, 90, 0)
Bill <- c(30, 30, 30, 30)
Holly <- c(15, 0, 90, 0)

student_list <- list(Marsha, Bill, Holly)

boxplot(student_list, xlab = "Students", ylab = "Time Spent on Homework", main = "Comparing Time Student's Spent Doing Homework")
legend(1.6, 75, legend = c("1 = Marsha", "2 = Bill", "3 = Holly"), lty = 1.5, cex = 1)

```

## Problem 3 (Verzani problem 3.5)
*A group of nursing students take turns measuring some basic assessments. Their data is:*

|          | Temp | Pulse | Systolic | Diastolic |
|----------|------|-------|----------|-----------|
| Jackie   | 98.2 | 96    |  134     | 90        |
| Florence | 98.6 | 56    |  120     | 80        |
| Mildred  | 98.2 | 76    |  150     | 95        |

*Create a data frame of these values. Will `plot()` and `boxplot()` produce the same graphic?*

```{r, tidy=TRUE, error=TRUE}
# Your code here
temp <- c(98.2, 98.6, 98.2)
pulse <- c(96, 56, 76)
systolic <- c(134, 120, 150)
diastolic <- c(90, 80, 95)

vitals_list <- list("Temp" = temp, "Pulse" = pulse, "Systolic" = systolic, "Diastolic" = diastolic)
vitals_df <- as.data.frame(vitals_list, stringsAsFactors = FALSE)

plot(vitals_df)
boxplot(vitals_df)

```

## Problem 4 (Verzani problem 3.8)
*The second argument to `split` can be a list of factors. The result is that all interactions (possible combinations) are used for the groups. In the `ToothGrowth` data set, growth (`len`) is measured for two types of supplements (`supp`) and three doses (`dose`). Split this `len` value into 6 groups.*

```{r, tidy=TRUE, error=TRUE}
# Your code here
with(ToothGrowth, split(len, dose))
with(ToothGrowth, split(len, supp))
```

## Problem 5 (Verzani problem 3.17)
*The `state.x77` data set contains various information for each of the fifty United States. We wish to explore possible relationships among the variables. First, we make the data set easier to work with by turning it into a data frame.*

```{r}
x77 <- data.frame(state.x77)
```

*Now, make scatter plots of `Population` and `Frost`; `Population` and `Murder`; `Population` and `Area`; and `Income` and `HS.Grad`. Do any relationships appear linear? Are there any surprising correlations?*

```{r, tidy=TRUE}
# Your code here
ggplot(x77, aes(x = Frost, y = Population)) + geom_point()
ggplot(x77, aes(x = Murder, y = Population)) + geom_point()
ggplot(x77, aes(x = Area, y = Population)) + geom_point()
ggplot(x77, aes(x = Income, y = Population)) + geom_point()
ggplot(x77, aes(x = HS.Grad, y = Population)) + geom_point()

cor(x77)

```
